---
title: "focus_afghanistan_eurostat"
author: "ynux"
date: "August, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

### Fokus Afghanistan, with Eurostat Data

Let's have a look at first decisions on asylum requests from Afghan citizens, in Europe. 

This means that we use the dataset `migr_asydcfsta`: "First instance decisions on applications by citizenship, age and sex Annual aggregated data (rounded)". (Remark: For Germany, these are the the BAMF decisions. Don't confuse this with the "first instance" in the legal system of Germany, that would be the Verwaltungsgericht.) (Second Remark: There's also quarterly data, we can work with this later.)


This data covers the years from 2008 to 2017 (as of August 2018). It's quite big - 85 MB, and 13'311'070 values. Loading this takes some minutes on my pretty strong laptop. We start with a reduced data set that was pulled and saved with the following code:

    library(eurostat)
    migr_asydcfsta=get_eurostat("migr_asydcfsta")
    saveRDS(migr_asydcfsta, file="/tmp/migr_asydcfsta_20180812.rds")

The data covers 32 European countries (`geo`). Some don't have enough data to do useful analysis. Let's ignore them.

In the code below, we reduce our data to:
   * Only totals in age and sex
   * only Afghanistan
   * only 2017 (for now)
   * only European countries with at least 500 decisions in 2017 
   * only columns of interest


```{r get_data, echo=FALSE, results="hide"}
library(knitr)
library(dplyr)
migr_asydcfsta=readRDS(file="/tmp/migr_asydcfsta_20180812.rds")
```

Let's have a quick look at what we have.
```{r look_at_full_data}
# The first few rows:
glimpse(migr_asydcfsta)
# Some first statistics, also showing the categories (sex, age, decisions):
summary(migr_asydcfsta)
```
This is too much information. Let's reduce it:
```{r reduce_data_total}
cutoff=3000
major_geo_total=filter(migr_asydcfsta, values > cutoff, time == "2017-01-01", decision == "TOTAL", sex == "T", age == "TOTAL", citizen == "AF", geo != "EU28", geo != "TOTAL") %>% 
  select(geo,values) %>%
  arrange(desc(values))
```

### A first look into the data
    
```{r look_at_major_total}
# The first few rows
View(major_geo_total)
```

### Reducing to the relevant deciding countries

OK, this is what we'll be working with. 

The first question is: How much information did we lose when ignoring countries with less than 500 decisions? 

Looking at the number of decisions per country brought the first surprise for me. In 2017, there were 15 countries with more than 1000 decisions on asylum application from Afghan citizens. All other 17 countries account for only 18972 decisions. (If you cut off at 1000 decisions, it's only 580)

In total there were 184'265 decisions. 

```{r other_geo_total}
    other_geo_total=filter(migr_asydcfsta, values <= cutoff, time == "2017-01-01", decision == "TOTAL", sex == "T", age == "TOTAL", citizen == "AF", geo != "EU28", geo != "TOTAL") %>%  arrange(desc(values))
dec_others <- sum(other_geo_total$values)
```

If you don't believe this, great. Lack of trust in data is a good thing. You can look it up at [eurostat migr_asydcfsta]( http://appsso.eurostat.ec.europa.eu/nui/show.do?dataset=migr_asydcfsta&lang=en/)
Our relevant countries are now:
```{r show_major_geo_total}
View(major_geo_total)
```
These are the country codes. The country labels can be found [here](http://dd.eionet.europa.eu/vocabulary/eurostat/geo/view). Normally, it's possible to get the labels with label_eurostat, but there seems to be an issue with this presently. xxx do this part later xxx
xxx XX is the rest xxx
xxx no Spain, no 

## Pie of European Countries, decisions in 2017 on asylum cases Afghanistan

```{r geo_decision_pie}
library(ggplot2)
# some technical workarounds for adding the row with the others (XX),
# and for sorting
major_geo_total$geo <- as.character(major_geo_total$geo)
all_geo_total <- rbind(major_geo_total, c("XX",dec_others))
all_geo_total$values <- as.numeric(all_geo_total$values) 
all_geo_total$geo <- factor(all_geo_total$geo, levels = arrange(all_geo_total, values)$geo)

geo_dec_pie <- ggplot(all_geo_total, aes(x="", y=values, fill=geo)) + geom_col(colour = "black") + coord_polar("y", start=0) + scale_fill_grey(start = 0.4, end = 0.9) + ggtitle ("Decisions on Afghan asylum Cases 2017", subtitle = "EU countries")
geo_dec_pie
```

```{r show_values_table}
View(major_geo_total)

```
xxx compare population of these EU countries? histogram xxx

## The Decisions: GENCONV + HUMSTAT + SUB_PROT + TEMP_PROT + REJECTED = TOTAL_POS + REJECTED = TOTAL

Now, how did our 15 countries decide in 2017? We reduced too much in the previous step, we need all the decisions now, not only the TOTAL.

```{r reduce_data}
major_geo <-filter(migr_asydcfsta, values > cutoff, time >= "2017-01-01", sex == "T", age == "TOTAL", citizen == "AF", geo != "EU28", geo != "TOTAL") %>% 
  select(geo,decision,values) %>%
  arrange(desc(values))

dec_bar <- ggplot(filter(major_geo, decision != "TOTAL")) + geom_col(aes(x=geo, y=values, fill=decision), colour="black") + scale_fill_grey()
dec_bar
```
