---
title: "eurostat_asylum_data_sources"
author: "ynux"
date: "May 27, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Eurostat Asylum Data Sources

First, you want to know which eurostat dataset or table to use. Our main sources are:

Dataset Code            | Dataset Shortname                   | Number of values as of May 2017
------------------------| ------------------------------------|----------------------------------
 migr_asyappctza        | applications, annual                |                         3'033'853
 migr_asyappctzm        | applications, monthly               |                        37'833'549
 migr_asydcfstq         | First instance decisions, quarterly |                        46'153'986
 migr_asydcfsta         | First instance decisions, annual    |                        11'163'156
 

How do you find all the eurostat sources on asylum? First, you can download it the native way from http://ec.europa.eu/eurostat/estat-navtree-portlet-prod/BulkDownloadListing?sort=1&file=dic%2Fde%2Ftable_dic.dic. This is also useful to double check if you found all the relevant sources.7
From this, we expect on "asylum" and "resettlement" 17 MIGR_ASY datasets, and 6 TPS tables, = 24 data sources.

With R eurostat:

```{r tables_and_datasets}

library(knitr)
library(eurostat)

eurostat_data_asyl <- search_eurostat("syl",type="all")
# Some of the asylum datasets don't have "asylum" in their description:
eurostat_data_dec <- search_eurostat("decisions on appl",type="all")
eurostat_data_withdrawn <- search_eurostat("withdraw", type="all")
eurostat_data_resettle <- search_eurostat("Resettled persons ", type="all")
eurostat_data_sources <- rbind(eurostat_data_asyl, eurostat_data_dec, eurostat_data_resettle, eurostat_data_withdrawn)
# now we have duplicates
eurostat_data_sources_u <- unique.data.frame(eurostat_data_sources)
eurostat_data_asyl_sorted <- subset(eurostat_data_sources_u[order(eurostat_data_sources_u$code),], type != "folder")
# Do we get the 23 rows that we expect?
dim(eurostat_data_asyl_sorted)

kable(eurostat_data_asyl_sorted, title="Eurostat Data Sources on Asylum")
```

Some of these are big. Unfortunately, the "values" column isn't filled the number of lines. It can be seen when looking the table up in the browser, as in 
http://appsso.eurostat.ec.europa.eu/nui/show.do?dataset=migr_asydcfstq&lang=en
and then choosing the "information" icon http://ec.europa.eu/eurostat/estat-navtree-portlet-prod/NodeInfoServices?lang=en&code=migr_asydcfstq


For details and background information, go to pages like
http://ec.europa.eu/eurostat/cache/metadata/en/migr_asyapp_esms.htm

There are more sources on "Dublin" cases.
